---
title: "Text modeling -- rstudio::conf 2020"
date: "2020/01/28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Welcome to day #2!

## Topic modeling

First download data to use in modeling:

https://www.gutenberg.org/browse/scores/top

Replace one to four of the books below with your own choice(s).

```{r}
library(tidyverse)
library(gutenbergr)

titles <- c("Twenty Thousand Leagues under the Sea", 
            "The War of the Worlds",
            "Pride and Prejudice", 
            "Great Expectations")

books <- gutenberg_works(title %in% titles) %>%
  gutenberg_download(meta_fields = "title")
```

What do you predict will happen if we run the following code?

**PREDICT WITH YOUR NEIGHBOR BEFORE YOU RUN**

```{r}
by_chapter <- books %>%
  group_by(title) %>%
  mutate(chapter = cumsum(str_detect(text, 
                                     regex("^chapter ", 
                                           ignore_case = TRUE)))) %>%
  ungroup() %>%
  filter(chapter > 0) %>%
  unite(document, title, chapter)

by_chapter
```

Someone has TORN YOUR BOOKS APART!!!

## Let's use topic modeling to put your books back together

As a first step, let's tokenize and tidy these chapters.

```{r}
library(tidytext)

word_counts <- by_chapter %>%
  ___ %>%
  anti_join(___) %>%
  count(document, word, sort = TRUE)

word_counts
```

Next, let's **cast** to a sparse matrix. 

How many features and observations do you have?

```{r}
words_sparse <- word_counts %>%
  ___(document, word, n)

___(words_sparse)
___(words_sparse)
```

Train a topic model.

```{r}
library(stm)

topic_model <- stm(___, K = 4, 
                   init.type = "Spectral")

summary(topic_model)
```

## Explore the output of topic modeling

The word-topic probabilities are called the "beta" matrix.

```{r}
chapter_topics <- tidy(topic_model, ___)

chapter_topics
```

What are the highest probability words in each topic?

**U N S C R A M B L E**

```{r}
top_terms <- chapter_topics %>%

ungroup() %>%

group_by(topic) %>%

arrange(topic, -beta)

top_n(10, beta) %>%
```

Let's build a visualization.

```{r}
top_terms %>%
  mutate(term = fct_reorder(term, beta)) %>%
  ggplot(___) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()
```

The document-topic probabilities are called "gamma".

```{r}
chapters_gamma <- tidy(topic_model, ___,
                       document_names = rownames(words_sparse))

chapters_gamma
```

How well did we do in putting our books back together into the 4 topics?

What do you predict will happen if we run the following code?

**PREDICT WITH YOUR NEIGHBOR BEFORE YOU RUN**

```{r}
chapters_parsed <- chapters_gamma %>%
  ___(document, c("title", "chapter"), 
           sep = "_", convert = TRUE)

chapters_parsed
```

Let's visualize the results.

**U N S C R A M B L E**

```{r}
chapters_parsed %>%

ggplot(aes(factor(topic), gamma)) +

facet_wrap(~ title)

mutate(title = fct_reorder(title, gamma * topic)) %>%

geom_boxplot() +
```


## Text classification

Let's get two texts and build a model to distinguish between them.

Replace one or two of the books below with your own choice(s).

```{r}
titles <- c("The War of the Worlds",
            "Pride and Prejudice")

books <- gutenberg_works(title %in% titles) %>%
  gutenberg_download(meta_fields = "title") %>%
  mutate(document = row_number())

books
```

By making the `document` column and using that as our modeling unit, we are splitting each book up until its individual lines, as given to us by Project Gutenberg.

Next, let's make a tidy, tokenized dataset.

```{r}
tidy_books <- books %>%
  unnest_tokens(word, text) %>%
  group_by(word) %>%
  filter(n() > 10) %>%
  ungroup

tidy_books
```

What do you predict will happen if we run the following code?

**PREDICT WITH YOUR NEIGHBOR BEFORE YOU RUN**

```{r}
library(rsample)

books_split <- tidy_books %>%
  select(document) %>%
  ___

train_data <- training(books_split)
test_data <- testing(books_split)
```

Next build:

- a sparse matrix with the features to use in modeling
- a dataframe with the **response** variable (i.e. title)

```{r}
sparse_words <- tidy_books %>%
  count(document, word, sort = TRUE) %>%
  inner_join(___) %>%
  ___

class(sparse_words)
dim(sparse_words)
```

## Build a dataframe with the response variable

```{r}
word_rownames <- as.integer(___)

books_joined <- tibble(document = word_rownames) %>%
  left_join(books %>%
              select(document, title))

books_joined
```


## Train a regularized regression model

```{r}
library(glmnet)

is_jane <- books_joined$title == "Pride and Prejudice"
model <- cv.glmnet(___, ___, 
                   family = "binomial", 
                   keep = TRUE)
```

You can also check out the built-in `plot(model)` results from glmnet.

## Understand and evaluate the model

How does the glmnet model classify each document?

```{r}
library(broom)

coefs <- model$glmnet.fit %>%
  ___ %>%
  filter(lambda == model$lambda.1se)

Intercept <- coefs %>%
  filter(term == "(Intercept)") %>%
  ___
```

**U N S C R A M B L E**

```{r}
classifications <- tidy_books %>%

mutate(probability = plogis(Intercept + score))

inner_join(test_data) %>%

group_by(document) %>%

inner_join(coefs, by = c("word" = "term")) %>%

summarize(score = sum(estimate)) %>%
```

What are the coefficients? Which ones contribute the most?

**U N S C R A M B L E**

```{r}
coefs %>%

group_by(estimate > 0) %>%

coord_flip()

geom_col(show.legend = FALSE) +

ungroup %>%

top_n(10, abs(estimate)) %>%

ggplot(aes(fct_reorder(term, estimate), 
           estimate, 
           fill = estimate > 0)) +
```

What do you predict will happen if we run the following code?

**PREDICT WITH YOUR NEIGHBOR BEFORE YOU RUN**

```{r}
comment_classes <- classifications %>%
  ___(books %>%
              select(title, document), by = "document") %>%
  mutate(title = as.factor(title))

comment_classes
```

Let's build an ROC ([receiver operating characteristic](https://en.wikipedia.org/wiki/Receiver_operating_characteristic)) curve.

```{r}
library(yardstick)

comment_classes %>%
  ___ %>%
  ggplot(aes(x = 1 - specificity, y = sensitivity)) +
  geom_line(size = 1.5) +
  geom_abline(
    lty = 2, alpha = 0.5,
    color = "gray50",
    size = 1.2
  )
```

What is the AUC?

```{r}
comment_classes %>%
  ___
```

What about a confusion matrix?

```{r}
comment_classes %>%
  mutate(
    prediction = case_when(
      probability > 0.5 ~ "Pride and Prejudice",
      TRUE ~ "The War of the Worlds"
    ),
    prediction = as.factor(prediction)
  ) %>%
  ___
```

Now let's talk about misclassifications.

```{r}
comment_classes %>%
  filter(
    ___,
    ___
  ) %>%
  sample_n(10) %>%
  inner_join(books %>%
               select(document, text)) %>%
  select(probability, text)
```

How should you change this code to see the **other** kind of misclassification?

**GO EXPLORE REAL-WORLD TEXT!**

Thanks for coming! <3
